### 2018-06-19 Maths Notes/Core/C3/Cheat sheet/C3 Cheat Sheet.tex
C3 Cheat Sheet
C3 Notes update

$a\cos\theta\pm b\sin\theta$ can be expressed in the form $R\sin(\theta\mp\alpha)$\\

@@

>>>>

$a\cos\theta\pm b\sin\theta$ can be expressed in the form $R\cos(\theta\mp\alpha)$\\

@@

\subsection{Parallel to the y axis}
For a line to be parallel to the y axis, the gradient must be infinite, this would arise from dividing by zero, so if the function does this, the value at x at which this occurs is the tangent
